---
title: "Federal Elections 2023"
subtitle: "Data Documentation"
author: "Swiss Federal Statistical Office | Politics, Culture, Media Section | Contact: poku@bfs.admin.ch"
date: "Last update: `r format(Sys.time(), '%d/%m/%y, %H:%M')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = FALSE)
library(readxl)
library(knitr)
library(kableExtra)
```


```{r include=FALSE}
library(readxl)
#Var-Tabellen einlesen
codebook_WBet <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "wahlbeteiligung", col_names = TRUE))
codebook_Kand <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "kandidierende", col_names = TRUE))
codebook_Part <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "parteien", col_names = TRUE))
codebook_List <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "listen", col_names = TRUE))
codebook_ZR_F_B <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "zeitreihen-frauen-beteiligung", col_names = TRUE))
codebook_ZR_P <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "zeitreihen-parteien", col_names = TRUE))
codebook_List_Gde <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "listen-gde", col_names = TRUE))
codebook_SRW <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "SRW", col_names = TRUE))

```

<br>

### Intro

The FSO is responsible for publishing the official provisional elections results of the federal elections. This documentation focuses on the dataset [Federal elections 2023](https://opendata.swiss/dataset/eidg-wahlen-2023) which contains the continuously updated result files on Election Sunday, October 22, 2023.


**Testing**: For testing purposes, a dataset exists on the DEV environment of opendata.swiss. Test data will be uploaded there several times until election Sunday. More information will follow in the associated data description (please subscribe to the dataset to receive update notifications). \
DEV-environment: https://ogdch-abnahme.clients.liip.ch/de/dataset/eidg-wahlen-2023



<br>

### Example data


Currently, 3 provisional test data sets with dummy results from the 2019 elections (National Council) are available. Description and test data for the Council of States will follow. \
(Go to "View Raw" for download ) \

**Note**: Status of test data: June 2023. Please refer to the changelog for the latest changes: https://bfspoku.github.io/wd-poku/Changelog_Eidgwahlen2023.html \


  1. Empty files. Structure of the files before election day.\
    <https://github.com/bfspoku/wd-poku/blob/ce1f3f26371e947d8ce94abd95a45112d6f1c249/docs/files/Testdata1.zip> 
    
  2. Structure of the files during election day (with partial results). 
      + Canton LU complete & confirmed
      + Canton BL intermediate status: 28/86 municipalities completed
      + remaining cantons empty\
    
     <https://github.com/bfspoku/wd-poku/blob/ce1f3f26371e947d8ce94abd95a45112d6f1c249/docs/files/Testdata2.zip> 
    
  3. Structure of the files after the election has been completed. \
    <https://github.com/bfspoku/wd-poku/blob/ce1f3f26371e947d8ce94abd95a45112d6f1c249/docs/files/Testdata3.zip> 
  

  
  
<hr style="border:1px solid black">

\

### NEW: JSON Listen-gde \
(Listes/Liste/Lists) \

20230926: New JSON with list results at municipality level. Update interval: continuously. \
(Unlike the other files, the file is not offered with an empty structure. Before 12.00 noon on election day, the file will be completely empty (0KB). ) 

Please read the following description.

\

Content description for the file: sd-t-17.02-NRW2023-listen-gde.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_List_Gde) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "40em", background = "#D3D3D3")
```

\

### JSON Wahlbeteiligung \
(Participation/Partecipazione/Turnout) \


\

Content description for the file: sd-t-17.02-NRW2023-wahlbeteiligung.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_WBet) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "40em", background = "#D3D3D3")
```

\

### JSON Kandidierende \
(Candidats/Candidati/Candidates) \



\

Content description for the file: sd-t-17.02-NRW2023-kandidierende.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_Kand) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "40em", background = "#D3D3D3")
```

\

### JSON Parteien \
(Partis/Partiti/Parties) \



\

Content description for the file: sd-t-17.02-NRW2023-parteien.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_Part) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "40em", background = "#D3D3D3")
```

\

### JSON Listen \
(Listes/Liste/Lists) \



\

Content description for the file: sd-t-17.02-NRW2023-listen.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_List) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "40em", background = "#D3D3D3")
```

\

### JSON Zeitreihen-frauen-beteiligung \
(Séries temporelles participation-femmes/Serie temporale partecipazione-donne/Time series participation-women) \



\

Content description for the file: sd-t-17.02-NRW2023-zeitreihen-frauen-beteiligung.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_ZR_F_B) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "40em", background = "#D3D3D3")
```

\

### JSON Zeitreihen-parteien \
(Séries temporelles partis/Serie temporale parti/Time series parties) \



\

Content description for the file: sd-t-17.02-NRW2023-zeitreihen-parteien.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_ZR_P) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "30em", background = "#D3D3D3")
```

\


### JSON SR - Kandidierende \
(CE - Candidats/CS - Candidati) \

\

Results of the elections to the Council of States are provided in the following formats:

* sd-t-17.02-SRW2023-candidates_first-round_election.json: results of the 1st round of elections
* sd-t-17.02-SRW2023-candidates_second-round.json: results of the 2nd round of elections

```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_SRW) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "30em", background = "#D3D3D3")
```

\
