---
title: "codebook_elections2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = FALSE)
library(readxl)
library(knitr)
library(kableExtra)
```


```{r include=FALSE}
library(readxl)
#Var-Tabellen einlesen
codebook_WBet <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "wahlbeteiligung", col_names = TRUE))
codebook_Kand <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "kandidierende", col_names = TRUE))
codebook_Part <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "parteien", col_names = TRUE))
codebook_List <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "listen", col_names = TRUE))

```


### Intro
Description of the dataset on the official provisional election results for the 2023 federal elections on opendata.swiss.
Currently, only a provisional test data set with dummy results of the 2019 elections is available on opendata.swiss: 

Test data set: <https://ogdch-abnahme.clients.liip.ch/de/dataset/eidgenossische-wahlen-2023-testing>

In the following, the characteristics of these files are described.
For this purpose, 3 different states are provided as test data for each file: \
  1. empty files. State how the file looks like before the election day.\
  2. state, how the file looks like with partial results during the election day.\
  3. state how the file looks like at the end of the election.\
  
  **Warning**: The file structures of the JSONs here are currently NOT yet final. Any changes to these files will be published on this page and in the          changelog on opendata.swiss.
  \

<hr style="border:1px solid black">

\

### JSON Wahlbeteiligung \
(Wahlbeteiligung/Participation/Partecipazione/Turnout) \

Testdataset1: <https://www-tmp-a.bfs.admin.ch/bfsstatic/dam/assets/23185013/master> \
Testdataset2:   \
Testdataset3:   \

\

Content description for the file: sd-t-17.02-NRW2023-wahlbeteiligung.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_WBet) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "30em", background = "#D3D3D3")
```

\

### JSON Kandidierende \
(Kandidierende/Candidats/Candidati/Candidates) \

Testdataset1: <https://www-tmp-a.bfs.admin.ch/bfsstatic/dam/assets/23185004/master> \
Testdataset2:   \
Testdataset3:   \

\

Content description for the file: sd-t-17.02-NRW2023-kandidierende.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_Kand) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "30em", background = "#D3D3D3")
```

\

### JSON Parteien \
(Parteien/Partis/Partiti/Parties) \

Testdataset1: <https://www-tmp-a.bfs.admin.ch/bfsstatic/dam/assets/23185009/master> \
Testdataset2:   \
Testdataset3:   \

\

Content description for the file: sd-t-17.02-sd-t-17.02-NRW2023-parteien.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_Part) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "30em", background = "#D3D3D3")
```

\

### JSON Listen \
(Listen/Listes/Liste/Lists) \

Testdataset1: <https://www-tmp-a.bfs.admin.ch/bfsstatic/dam/assets/23185010/master> \
Testdataset2:   \
Testdataset3:   \

\

Content description for the file: sd-t-17.02-NRW2023-listen.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_List) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "30em", background = "#D3D3D3")
```

\
