---
title: "codebook_elections2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = FALSE)
library(readxl)
library(knitr)
library(kableExtra)
```


```{r include=FALSE}
library(readxl)
#Var-Tabellen einlesen
codebook_WBet <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "wahlbeteiligung", col_names = TRUE))
codebook_Kand <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "kandidierende", col_names = TRUE))
codebook_Part <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "parteien", col_names = TRUE))
codebook_List <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "listen", col_names = TRUE))
codebook_ZR_F_B <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "zeitreihen-frauen-beteiligung", col_names = TRUE))
codebook_ZR_P <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "zeitreihen-parteien", col_names = TRUE))
```


### Intro
Description of the dataset on the official provisional election results for the 2023 federal elections on [opendata.swiss](https://ogdch-abnahme.clients.liip.ch/de/dataset/eidg-wahlen-2023).



Currently, 3 provisional test data sets with dummy results from the 2019 elections (National Council) are available: \
(Description and test data for the Council of States will follow.) \ 

  1. empty files. State how the file looks like before the election day.\
    <https://github.com/bfspoku/wd-poku/blob/3745e9c45d4bc76b0416b639aa7fa1c994defa7b/docs/files/Testdata1.zip> \
    
  2. state, how the file looks like with partial results during the election day.\
    URL..... \
    
  3. state how the file looks like at the end of the election.\
    URL..... \
  
  In the following, the characteristics of these files are described.
  
  **Warning**: The file structures of the JSONs here are currently NOT yet final. Any changes to these files will be published on this page and in the changelog on opendata.swiss.
  \
  
Responsible for data set: Swiss Federal Statistical Office | 
Section Politics, Culture, Media | 
Contact: poku@bfs.admin.ch \   

<hr style="border:1px solid black">

\

### JSON Wahlbeteiligung \
(Participation/Partecipazione/Turnout) \


\

Content description for the file: sd-t-17.02-NRW2023-wahlbeteiligung.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_WBet) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "30em", background = "#D3D3D3")
```

\

### JSON Kandidierende \
(Candidats/Candidati/Candidates) \



\

Content description for the file: sd-t-17.02-NRW2023-kandidierende.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_Kand) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "30em", background = "#D3D3D3")
```

\

### JSON Parteien \
(Partis/Partiti/Parties) \



\

Content description for the file: sd-t-17.02-sd-t-17.02-NRW2023-parteien.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_Part) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "30em", background = "#D3D3D3")
```

\

### JSON Listen \
(Listes/Liste/Lists) \



\

Content description for the file: sd-t-17.02-NRW2023-listen.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_List) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "30em", background = "#D3D3D3")
```

\

### JSON Zeitreihen-frauen-beteiligung \
(Séries temporelles participation-femmes/Serie temporale partecipazione-donne/Time series participation-women) \



\

Content description for the file: sd-t-17.02-NRW2023-zeitreihen-frauen-beteiligung.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_ZR_F_B) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "30em", background = "#D3D3D3")
```

\

### JSON Zeitreihen-parteien \
(Séries temporelles partis/Serie temporale parti/Time series parties) \



\

Content description for the file: sd-t-17.02-NRW2023-zeitreihen-parteien.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_ZR_P) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "30em", background = "#D3D3D3")
```

\
