---
title: "Federal Elections 2023"
subtitle: "Data Documentation"
author: "Swiss Federal Statistical Office | Politics, Culture, Media Section | Contact: poku@bfs.admin.ch"
date: June 22, 2023
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = FALSE)
library(readxl)
library(knitr)
library(kableExtra)
```


```{r include=FALSE}
library(readxl)
#Var-Tabellen einlesen
codebook_WBet <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "wahlbeteiligung", col_names = TRUE))
codebook_Kand <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "kandidierende", col_names = TRUE))
codebook_Part <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "parteien", col_names = TRUE))
codebook_List <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "listen", col_names = TRUE))
codebook_ZR_F_B <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "zeitreihen-frauen-beteiligung", col_names = TRUE))
codebook_ZR_P <- as.data.frame(read_xlsx("codebook/codebook_elections2023.xlsx", sheet = "zeitreihen-parteien", col_names = TRUE))
```

<br>

### Intro

The FSO is responsible for publishing the official provisional elections results of the federal elections. This documentation focuses on the dataset [Federal elections 2023](https://ogdch-abnahme.clients.liip.ch/de/dataset/eidg-wahlen-2023) (currently DEV environment) which contains the continuously updated result files on Election Sunday, October 22, 2023. 



**Note**: The structure of the JSON files is still under review and has not been finally defined yet. Any changes to these files will be published on this page and in the changelog on opendata.swiss. For demonstration purposes, the dataset is currently linked on the DEV environment of opendata.swiss. The final files will be made available at the following URL: [PROD LINK opendata.swiss]


<br>

### Example data


Currently, 3 provisional test data sets with dummy results from the 2019 elections (National Council) are available. Description and test data for the Council of States will follow. \
(Go to "View Raw" for download ) \ 

  1. Empty files. Structure of the files before election day.\
    <https://github.com/bfspoku/wd-poku/blob/ce1f3f26371e947d8ce94abd95a45112d6f1c249/docs/files/Testdata1.zip> 
    
  2. Structure of the files during election day (with partial results). 
      + Canton LU complete & confirmed
      + Canton BL intermediate status: 28/86 municipalities completed
      + remaining cantons empty\
    
     <https://github.com/bfspoku/wd-poku/blob/ce1f3f26371e947d8ce94abd95a45112d6f1c249/docs/files/Testdata2.zip> 
    
  3. Structure of the files after the election has been completed. \
    <https://github.com/bfspoku/wd-poku/blob/ce1f3f26371e947d8ce94abd95a45112d6f1c249/docs/files/Testdata3.zip> 
  

  
  
<hr style="border:1px solid black">

\

### JSON Wahlbeteiligung \
(Participation/Partecipazione/Turnout) \


\

Content description for the file: sd-t-17.02-NRW2023-wahlbeteiligung.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_WBet) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "40em", background = "#D3D3D3")
```

\

### JSON Kandidierende \
(Candidats/Candidati/Candidates) \



\

Content description for the file: sd-t-17.02-NRW2023-kandidierende.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_Kand) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "40em", background = "#D3D3D3")
```

\

### JSON Parteien \
(Partis/Partiti/Parties) \



\

Content description for the file: sd-t-17.02-NRW2023-parteien.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_Part) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "40em", background = "#D3D3D3")
```

\

### JSON Listen \
(Listes/Liste/Lists) \



\

Content description for the file: sd-t-17.02-NRW2023-listen.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_List) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "40em", background = "#D3D3D3")
```

\

### JSON Zeitreihen-frauen-beteiligung \
(Séries temporelles participation-femmes/Serie temporale partecipazione-donne/Time series participation-women) \



\

Content description for the file: sd-t-17.02-NRW2023-zeitreihen-frauen-beteiligung.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_ZR_F_B) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "40em", background = "#D3D3D3")
```

\

### JSON Zeitreihen-parteien \
(Séries temporelles partis/Serie temporale parti/Time series parties) \



\

Content description for the file: sd-t-17.02-NRW2023-zeitreihen-parteien.json
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(codebook_ZR_P) %>% kable_paper(full_width = F) %>%
  column_spec(1, bold = T, border_right = T) %>%
  column_spec(2, bold = T, border_right = T) %>%
  column_spec(3, bold = F, border_right = T) %>% 
  column_spec(4, width = "30em") %>% 
  column_spec(5, width = "30em", background = "#D3D3D3")
```

\
