---
title: "Federal Elections 2023"
subtitle: "Info"
author: "Swiss Federal Statistical Office | Politics, Culture, Media Section | Contact: poku@bfs.admin.ch"
date: "Last update: `r format(Sys.time(), '%d/%m/%y, %H:%M')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = FALSE)
library(readxl)
library(knitr)
library(kableExtra)
```

```{r include=FALSE}
library(readxl)
#Var-Tabellen einlesen
data_intervals <- as.data.frame(read_xlsx("codebook/data_intervals_elections2023.xlsx", col_names = TRUE))

```

\

## Info page FSO data set on opendata.swiss
Info page with updates on the Federal Statistical Office's data set for the Federal Elections 2023

\

**Productive data set:**https://opendata.swiss/dataset/eidg-wahlen-2023

**Testing data set:** https://ogdch-abnahme.clients.liip.ch/de/dataset/eidg-wahlen-2023

<hr style="border:1px solid black">
\

#### 20231019: Last minor changes (structure of the files is not affected)

1. Files with municipality level: In the canton BE, the municipality "Oberhünigen" (BFS-Nr. 629) now has its own ballot box and is therefore included in the files.

2. Based on the consultation with all the general secretariats of the parties regarding the attribution of the submitted electoral lists to national parties, the following change has been made:


| Canton    | liste_nummer_bfs | liste_nummer_kanton | liste_bezeichnung       | Party old | Party new |
|:---------:|:----------------:|:-------------------:|:------------------------:|:---------:|:---------:|
|  3 / LU   |         23       |        26           | Aktive Senioren Luzern  |  SVP       |  Others

\
<hr style="border:1px solid black">

\


#### 20230925: New Data Ressource sd-t-17.02-SRW2023-kandidierende_erster-wahlgang.json
JSON file for the results of the Council of States added to the test environment. This file already includes the candidates for the first round of voting on October 22. Results for the Council of States are updated per completed canton.\
Data description: https://bfspoku.github.io/wd-poku/codebook_elections2023.html#JSON_SR_-_Kandidierende_

\
<hr style="border:1px solid black">

\

#### 20230925: New Data Ressource sd-t-17.02-NRW2023-listen-gde.json
Due to corresponding demand (and after extensive internal testing), we offer a new JSON with list results at municipality level. This JSON will be continuously updated on election Sunday. \
There are some special aspects to be taken into account with this file. Please read the data description, which has been extended accordingly to include this file: https://bfspoku.github.io/wd-poku/codebook_elections2023.html#JSON_Listen_

\
<hr style="border:1px solid black">


#### 20230925: Test day on 28 September 2023
**Planned schedule for the test day on 28 September 2023**

On 28 September 2023 from 10.00 - 12.00 test files will be continuously uploaded on the DEV environment (https://ogdch-abnahme.clients.liip.ch/de/dataset/eidg-wahlen-2023)
Below is a brief overview of the schedule and test dates offered. <br> 
1. The test only includes the JSON files provided on election Sunday. <br> 
2. All files will already contain the official lists and candidates.(Exceptions are possible for cantons with a majoritarian electoral system without compulsory registration). <br>
3. A first set of test data will already be uploaded to the DEV environment on 25 September. This should facilitate the preparation for the test day. <br>
4. There will be intermediate results uploaded for several cantons, and for some there will also be a cantonal final result. The complete election results at the Swiss level will not be simulated. (Work on such a complete data set is underway, but it is still unclear whether this can be offered until election day. Corresponding information on further testing possibilities would be published here.)


**Overview test data** <br>
(May be changed at short notice.)

*National Council:*

* Intermediate results for the following cantons (FSO canton number): 1, 3, 9, 11, 13, 18, 20, 24, 26
* Final results for the following cantons: 1, 9, 11, 12, 20, 26

*Council of States:*

* Results for the first round in the following cantons: 1, 6, 16

\
<hr style="border:1px solid black">

#### 20230925: Cantonal delivery intervals on election Sunday \
(Indication of the cantons, without guarantee)
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(data_intervals) %>% kable_paper(full_width = F) %>%
  column_spec(1, border_right = T) %>%
  column_spec(2, border_right = T) %>%
  column_spec(3, border_right = T, width = "30em") %>% 
  column_spec(4, width = "30em")
```

