---
title: "Federal Elections 2023"
subtitle: "Info"
author: "Swiss Federal Statistical Office | Politics, Culture, Media Section | Contact: poku@bfs.admin.ch"
date: "Last update: `r format(Sys.time(), '%d/%m/%y, %H:%M')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = FALSE)
library(readxl)
library(knitr)
library(kableExtra)
```

```{r include=FALSE}
library(readxl)
#Var-Tabellen einlesen
data_intervals <- as.data.frame(read_xlsx("codebook/data_intervals_elections2023.xlsx", col_names = TRUE))

```

```{r include=FALSE}
library(readxl)
#Var-Tabellen einlesen
New_KandNr_ListPos <- as.data.frame(read_xlsx("codebook/Corr_KandNr_ListPos.xlsx", sheet = "New", col_names = TRUE))

```

```{r include=FALSE}
library(readxl)
#Var-Tabellen einlesen
Old_KandNr_ListPos <- as.data.frame(read_xlsx("codebook/Corr_KandNr_ListPos.xlsx", sheet = "Old", col_names = TRUE))

```

\

## Info page FSO data set on opendata.swiss
Info page with updates on the Federal Statistical Office's data set for the Federal Elections 2023

\

**Productive data set:**https://opendata.swiss/dataset/eidg-wahlen-2023

**Testing data set:** https://ogdch-abnahme.clients.liip.ch/de/dataset/eidg-wahlen-2023 (deactivated)

<hr style="border:1px solid black">
\

#### 20240524: Minor corrections in the context of data archiving

Corrections have no influence on the final result. \

* Modification of candidate numbers for liste_nummer_bfs=12 (liste_nummer_kanton=12) in canton GR (Correction in data supplied by the canton)
* Modification of the list positions of candidates in GR and AG

\
**NEW:** \

```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(New_KandNr_ListPos, align='lclcllcc') %>% kable_paper(full_width = F) %>%
  column_spec(1, border_right = T) %>%
  column_spec(2, border_right = T) %>%
  column_spec(3, border_right = T) %>% 
  column_spec(4, border_right = T) %>% 
  column_spec(5, border_right = T) %>% 
  column_spec(6, border_right = T) %>% 
  column_spec(7, border_right = T) %>% 
  column_spec(8, border_right = T) 
  
```

\

**OLD:** \
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(Old_KandNr_ListPos, align='lclcllcc') %>% kable_paper(full_width = F) %>%
  column_spec(1, border_right = T) %>%
  column_spec(2, border_right = T) %>%
  column_spec(3, border_right = T) %>% 
  column_spec(4, border_right = T) %>% 
  column_spec(5, border_right = T) %>% 
  column_spec(6, border_right = T) %>% 
  column_spec(7, border_right = T) %>% 
  column_spec(8, border_right = T) 
  
```


\

* FSO municipality number of the place of residence added (best effort)\
    JSON-file: sd-t-17.02-NRW2023-kandidierende.json \
    Variable: "wohnort_gemeinde_nummer" \
    
* With the data upload of 30 November, the variables indicating the number of municipalities with a result were no longer filled correctly. \
    JSON-files: multiple \
    Variable: gemeinden_abgeschlossen	\

<hr style="border:1px solid black">
\



#### 20231130: Upload of the final results
The final results have been uploaded. The published data includes the corrections provided by the cantons after election day.

<hr style="border:1px solid black">
\


#### 20231031: New Data Resource sd-t-17.02-SRW2023-kandidierende_zweiter-wahlgang.json
New resource on 2nd rounds of elections to the Council of States. Results are updated only once, on Monday after the election round.

<hr style="border:1px solid black">
\

#### 20231025: National Council elections: Error in published party strengths at national level

For further information, see [press release](https://www.bfs.admin.ch/bfs/en/home/news/press-releases.assetdetail.29025152.html). The following resources are affected by the correction:

*	sd-t-17.02-NRW2023-wahlbeteiligung.json
*	sd-t-17.02-NRW2023-wahlbeteiligung-appendix.csv
*	sd-t-17.02-NRW2023-parteien.json
*	sd-t-17.02-NRW2023-parteien-appendix.csv
*	sd-t-17.02-NRW2023-zeitreihen-parteien.json
*	sd-t-17.02-NRW2023-zeitreihen-parteien-appendix.csv

The corrections include the rectification of the aggregation error made by the FSO. The corrections received from the cantons are being collected and will be released in the course of the publication of the final results end of November.

<hr style="border:1px solid black">
\

#### 20231019: Last minor changes (structure of the files is not affected)

1. Files with municipality level: In the canton BE, the municipality "Rüti bei Lyssach" (BFS-Nr. 422) now has its own ballot box and is therefore included in the files.

2. Based on the consultation with all the general secretariats of the parties regarding the attribution of the submitted electoral lists to national parties, the following change has been made:


| Canton    | liste_nummer_bfs | liste_nummer_kanton | liste_bezeichnung       | Party old | Party new |
|:---------:|:----------------:|:-------------------:|:------------------------:|:---------:|:---------:|
|  3 / LU   |         23       |        26           | Aktive Senioren Luzern  |  SVP       |  Others

\
<hr style="border:1px solid black">

\


#### 20230925: New Data Resource sd-t-17.02-SRW2023-kandidierende_erster-wahlgang.json
JSON file for the results of the Council of States added to the test environment. This file already includes the candidates for the first round of voting on October 22. Results for the Council of States are updated per completed canton.\
Data description: https://bfspoku.github.io/wd-poku/codebook_elections2023.html#JSON_SR_-_Kandidierende_

\
<hr style="border:1px solid black">

\

#### 20230925: New Data Ressource sd-t-17.02-NRW2023-listen-gde.json
Due to corresponding demand (and after extensive internal testing), we offer a new JSON with list results at municipality level. This JSON will be continuously updated on election Sunday. \
There are some special aspects to be taken into account with this file. Please read the data description, which has been extended accordingly to include this file: https://bfspoku.github.io/wd-poku/codebook_elections2023.html#JSON_Listen_

\
<hr style="border:1px solid black">


#### 20230925: Test day on 28 September 2023
**Planned schedule for the test day on 28 September 2023**

On 28 September 2023 from 10.00 - 12.00 test files will be continuously uploaded on the DEV environment (https://ogdch-abnahme.clients.liip.ch/de/dataset/eidg-wahlen-2023)
Below is a brief overview of the schedule and test dates offered. <br> 
1. The test only includes the JSON files provided on election Sunday. <br> 
2. All files will already contain the official lists and candidates.(Exceptions are possible for cantons with a majoritarian electoral system without compulsory registration). <br>
3. A first set of test data will already be uploaded to the DEV environment on 25 September. This should facilitate the preparation for the test day. <br>
4. There will be intermediate results uploaded for several cantons, and for some there will also be a cantonal final result. The complete election results at the Swiss level will not be simulated. (Work on such a complete data set is underway, but it is still unclear whether this can be offered until election day. Corresponding information on further testing possibilities would be published here.)


**Overview test data** <br>
(May be changed at short notice.)

*National Council:*

* Intermediate results for the following cantons (FSO canton number): 1, 3, 9, 11, 13, 18, 20, 24, 26
* Final results for the following cantons: 1, 9, 11, 12, 20, 26

*Council of States:*

* Results for the first round in the following cantons: 1, 6, 16

\
<hr style="border:1px solid black">

#### 20230925: Cantonal delivery intervals on election Sunday \
(Indication of the cantons, without guarantee)
```{r, echo=FALSE}
library(kableExtra)
opts <- options(knitr.kable.NA = "")

kbl(data_intervals) %>% kable_paper(full_width = F) %>%
  column_spec(1, border_right = T) %>%
  column_spec(2, border_right = T) %>%
  column_spec(3, border_right = T, width = "30em") %>% 
  column_spec(4, width = "30em")
```

